Proof nets for first-order additive linear logic

### 2017-12-22 ALL1.tex
lutz' comments

For two witness labellings $\Sigma$ and $\Xi$ on the same linking $\lambda$, one is \defn{more general} than the other, $\Sigma\gen\Xi$, if $\Sigma(C,D)\gen\Xi(C,D)$ for every link $(C,D)\in\lambda$. We extend this to the linkings themselves: $\lambda_\Sigma\gen\lambda_\Xi$. Observe that for an axiom linking $\lambda$, the initial linking $\lambda_\star$ is the most general among the witness linkings $\lambda_\Sigma$ for any $\Sigma$.

>>>>

For two witness labellings $\Sigma$ and $\Xi$ on the same linking $\lambda$, one is \defn{more general} than the other, $\Sigma\gen\Xi$, \lutz{say which one is more general} if $\Sigma(C,D)\gen\Xi(C,D)$ for every link $(C,D)\in\lambda$. We extend this to the linkings themselves: $\lambda_\Sigma\gen\lambda_\Xi$. Observe that for an axiom linking $\lambda$, the initial linking $\lambda_\star$ is the most general among the witness linkings $\lambda_\Sigma$ for any $\Sigma$.
